---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753li0197)
```

# Introduction

The MATH4754li0197 package is a collection of functions and datasets that I have created to be used in the labs, projects, and assignments throughout this course. 

## First function

This function was taken and used in lab 5 to create a binomial simulation by making a binomial distribution plot

```{r}
MATH4753li0197::mybin(1000, n = 10, p = 0.5)
```
This plot is a binomial distribution with iter = 1000 iterations, n = 10 sample size, p = 0.5 probability of success



## Second function

This function was used in lab 4 and 
The function is used to calculate the intercept of a quadratic.
It is used to produce heights for input 'x' for it to be used on a plot to graph a quadratic

```{r}
MATH4753li0197::myplot(3)
```
This value can be used for the intercept of a quadratic.


## Third function


This function was used in lab 6 and is used to create a normal density distribution curve plot
```{r}
MATH4753li0197::myncurve(3, 7, 2)
```

It creates a normal density distribution curve where the parameters are mu = 3, sigma = 7, and it calculates the area under the curve.


## Fourth function

This function was used in lab 7 and is a documentation of the FIREDAM data set containing a data frame with 15 rows and 2 variable which is distance and damage.
```{r}
MATH4753li0197::fire
MATH4753li0197::ddt

```

